---
title: "Face detection and recognition inference pipeline"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Face detection and recognition inference pipeline}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

> Note: This is an R port of the original Tim Esler's tutorial [available here](https://github.com/timesler/facenet-pytorch/blob/master/examples/infer.ipynb).

The following example illustrates how to use the {facenet} R package to perform face detection and recogition on an image dataset using an `Inception Resnet V1` pretrained on the `VGGFace2 dataset`.

The following {torch} methods are included:

- Datasets
- Dataloaders
- GPU/CPU processing

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = identical(Sys.getenv("TORCH_TEST", unset = "0"), "1")
)
```

```{r setup}
library(torch)
library(torchvision)
library(facenet)
```

Determine if an nvidia GPU is avaliable
```{r}
device_type <- if(cuda_is_available()) "cuda" else "cpu"
device <- torch_device(device_type)
```

Running on device: `r device_type`

## Define MTCNN Module

Default params shown for illustration, but not needed. Note that, since MTCNN is a collection of neural nets and other code, the device must be passed in the following way to enable copying of objects when needed internally.

See `help(nn_mtcnn)` for more details.

```{r}
mtcnnet <- mtcnn(
  image_size = 160, margin = 0, min_face_size = 20,
  thresholds = c(0.6, 0.7, 0.7), factor = 0.709, post_process = TRUE,
  device = device
)
```

## Define Inception Resnet V1 module

Set `classify = TRUE` for pretrained classifier. For this example, we will use the model to output embeddings/CNN features. Note that for inference, it is important to set the model to eval mode.

See `help(nn_inception_resnet_v1)` for more details.

```{r}
resnet <- nn_inception_resnet_v1(pretrained = 'vggface2')$eval()$to(device = device)
```

## Define a dataset and data loader

We add the `idx_to_class` attribute to the dataset to enable easy recoding of label indices to identity names later one.

```{r}
collate_fn <- function(x) {
  return(x[[1]])
}

dataset <- torchvision::image_folder_dataset('../inst/test_images')
loader <- dataloader(dataset, collate_fn = collate_fn)
```


